### 2016-06-23 intro.tex
responding to JK's comments

First, we note that the security notion forbids~$A$ to win if it
outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a
false positive. 
\jnote{We discussed this on the phone, but let me
put it in writing here. I think this is actually a reasonable choice
because it captures the notion that ``even after finding some false
positives, it remains hard to find additional false positives.''
Note that in practice finding false positives is ``easy'' since
$\epsilon$ might be $1/1000$ rather than negligible.} 
\tsnote{For me the question is: is security violated once the first FP is found, or
the second?  My answer, which is in line with the traditional
soundness notion, is that the first FP is a security violation
even if finding it isn't ``hard'' by cryptographic standards.
But I do appreciate your point.  A natural goal is to say that, in some sense,
\emph{adaptivity doesn't make it any easier} to find a FP.  Adapting
to what, though?  In the traditional notion, $x$~is picked before the
coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions
are sampled.  The direct non-adaptive generalization is to say that
$x_1,x_2,\ldots,x_q$ are all picked up front.  The direct
\emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to
depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The
NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries,
but \emph{not} (directly) to the input-output behaviors of the hash
functions. }
\tsnote{Perhaps a more obvious way to capture the idea that ``finding
  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$n$, and say
that that the adversary wins iff it outputs~$n$ FPs (these may have
been previously queried to the set-membership oracle).  
Note that in the ROM (and probably in practice) finding~$n>1$ FPs will
require~$n$ times the work; finding the first won't help in finding
the second.} 
%\tsnote{Here's an off-the-wall idea.  What if the basic FP security
%notion gave the adversary an oracle for set-membership (and the hash functions, depending on the setting), and after interacting with these
%it is challenged with either $x_0$ or $x_1$, where $x_0$ is a random
%point from the set of non-FPs, and $x_1$ is a random point from the
%set of FPs?  (No oracles after being challenged.)  The adversary has
%to decide which it received.}

>>>>

First, we note that the security notion forbids~$A$ to win if it
outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a
false positive. 
\jnote{We discussed this on the phone, but let me
put it in writing here. I think this is actually a reasonable choice
because it captures the notion that ``even after finding some false
positives, it remains hard to find additional false positives.''
Note that in practice finding false positives is ``easy'' since
$\epsilon$ might be $1/1000$ rather than negligible.} 
\tsnote{For me the question is: is security violated once the first FP is found, or
the second?  My answer, which is in line with the traditional
soundness notion, is that the first FP is a security violation
even if finding it isn't ``hard'' by cryptographic standards.
But I do appreciate your point.  A natural goal is to say that, in some sense,
\emph{adaptivity doesn't make it any easier} to find a FP.  Adapting
to what, though?  In the traditional notion, $x$~is picked before the
coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions
are sampled.  The direct non-adaptive generalization is to say that
$x_1,x_2,\ldots,x_q$ are all picked up front.  The direct
\emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to
depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The
NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries,
but \emph{not} (directly) to the input-output behaviors of the hash
functions.  The three notions I've proposed in Figure 1 cover a
spectrum adaptivity: the first is adapting to set-membership queries
only, the second to those and hash input-output behavior, the third to
set-membership queries and full knowledge of the hash functions.  Each
has it's own associated (informal) security interpretation.}
\tsnote{Perhaps a more obvious way to capture the idea that ``finding
  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say
that that the adversary wins iff it outputs~$f$ FPs (these may have
been previously queried to the set-membership oracle).  
Note that in the ROM (and probably in practice) finding~$f>1$ FPs will
require~$f$ times the work.  Right?} 
%\tsnote{Here's an off-the-wall idea.  What if the basic FP security
%notion gave the adversary an oracle for set-membership (and the hash functions, depending on the setting), and after interacting with these
%it is challenged with either $x_0$ or $x_1$, where $x_0$ is a random
%point from the set of non-FPs, and $x_1$ is a random point from the
%set of FPs?  (No oracles after being challenged.)  The adversary has
%to decide which it received.}
